Considering scale in multilayer animal social networks

### 2020-06-23 paper/manuscript.Rmd
craters

## Caribou socioecology
Caribou are gregarious ungulates with fission-fusion dynamics [@Lesmerises_2018]
that display temporal and spatial variation in social networks [@Peignier_2019].
In winter, caribou dig holes in the snow, termed craters, to access forage
[@Bergerud_1974]. Cratering is presumed to be a costly behaviour and as a
result, caribou tend to occupy and re-use craters once they are established.
Importantly, craters exist on the landscape at multiple scales: the crater scale
(a single crater), the feeding area scale (multiple craters in close proximity),
and the winter range scale (all craters within an individual’s range)
[@Mayor_2009]. Access to forage is seasonally heterogeneous depending on snow
cover and, in winter, variable distribution of craters on the landscape.

>>>>

## Caribou socioecology
Caribou are gregarious ungulates with fission-fusion dynamics [@Lesmerises_2018]
that display temporal and spatial variation in social networks [@Peignier_2019].
In winter, caribou dig holes, termed craters, to access forage beneath the snow
[@Bergerud_1974]. Cratering is presumed to be a costly behaviour and as a
result, caribou tend to occupy and re-use craters once they are established.
Importantly, craters exist on the landscape at multiple scales: the crater scale
(a single crater), the feeding area scale (multiple craters in close proximity),
and the winter range scale (all craters within an individual’s range)
[@Mayor_2009]. Access to forage is therefore heterogeneous in winter 
depending on snow cover and distribution of craters on the landscape.
